\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%\usepackage{cases}
%% or use the graphicx package for more complicated commands
\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
\usepackage{epsfig}
%\usepackage{subfig}
\usepackage{comment}

@@

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=1500 (adaptive mesh)     
}
}     
\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a general trend/front that is also travelling towards the left-hand side.}
\label{fig:2testcase_c}
\end{figure}

\begin{figure}
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=end (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end (adaptive mesh)     
}
}     
\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh. When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
\label{fig:2testcase_d}
\end{figure}

@@

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR10 fixed mesh start    
}
\vspace{0.25cm}

\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 adapt mesh start     
}

\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (c) MR10 fixed mesh t=1500      
}

\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (d) MR10 adapt mesh t=1500     
}
}     
\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps}
\label{fig:3testcase_a}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (e) MR10 fixed mesh t=7500    
}
\vspace{0.25cm}

\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (f) MR10 adapt mesh t=7500      
}

\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (g) MR10 fixed mesh end      
}

\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (h) MR10 fixed adapt end]     
}
}     
\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h). When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
\label{fig:3testcase_b}
\end{figure}

\begin{figure}                
\centering
\includegraphics{./Pics1/5reg_dinlet_fixed_500.pdf}
\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_b}
\end{figure}

%\begin{comment}
%\begin{figure}
%\centering
%\subfigure[fixed mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}}\\[2mm]%
%\subfigure[adaptive mesh, t=500]{\includegraphics[width=0.75\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}}%
%\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
%\label{fig:3testcase_b}
%\end{figure}

\begin{comment}

\begin{figure}[h]
\makebox[\textwidth]{%
\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
\hfill    
\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
\hfill    
\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
}%
\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_b}
\end{figure}

>>>>

%% if you use PostScript figures in your article
%% use the gra

%%graphis package for simple commands
%% \usepackage{graphics}
%\usepackage{cases}
%% or use the graphicx package for more complicated commands
\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
\usepackage{epsfig}
%\usepackage{subfig}
\usepackage{comment}

@@

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=1500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=1500 (adaptive mesh)     
}
}     
\caption{Cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
\label{fig:2testcase_c}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) flow at t=end (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) flow at t=end (adaptive mesh)     
}
}     
\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh. When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
\label{fig:2testcase_d}
\end{figure}

@@

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_100.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) MR10 fixed mesh start    
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_start.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) MR10 adapt mesh start     
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (c) MR10 fixed mesh t=1500      
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_adapt_dinlet/5regions_dinlet_adapt_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (d) MR10 adapt mesh t=1500     
}
}     
\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps}
\label{fig:3testcase_a}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (e) MR10 fixed mesh t=7500    
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_adapt_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (f) MR10 adapt mesh t=7500      
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_fixed_end.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (g) MR10 fixed mesh end      
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.75\textwidth]{./Pics1/mr10_5regions_fixed_dinlet/5regions_dinlet_adapt_end.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (h) MR10 fixed adapt end     
}
}     
\caption{Comparing test-cases of fixed and adaptive mesh while we have a dual inlet, using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, t=250(a,b), t=500(c,d), t=1500(e,f), t=3000(g,h). When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
\label{fig:3testcase_b}
\end{figure}

\begin{figure}[h]
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (a) double inlet - fixed mesh   
}
\hbox{\hspace{3.5cm}
\includegraphics[width=.5\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{5.0cm} (b) double inlet adaptive mesh   
}
}     
\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
\label{fig:3testcase_b}
\end{figure}

%\begin{figure}[h]
%\makebox[\textwidth]{%
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
%\hfill    
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
%}\\[0.5cm]% If you want some vertical space
%\makebox[\textwidth]{%
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_fixed_500.pdf}%
%\hfill    
%\includegraphics[width=0.49\textwidth]{./Pics1/5reg_dinlet_adapt_500.pdf}%
%}%
%\caption{for t=$500$ there is a comparison between fixed mesh(a) and adaptive mesh(b).}
%\label{fig:3testcase_b}
%\end{figure}
